\documentclass[11pt,a4paper]{article}

% ================== PACKAGES ==================
\usepackage[a4paper,margin=1.8cm]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{setspace}
\usepackage{parskip}
\usepackage[T1]{fontenc}
\usepackage{lmodern}

% ================== SETTINGS ==================
\setstretch{1.15}
\setlist[itemize]{leftmargin=*, noitemsep, topsep=3pt}

\hypersetup{
  colorlinks=true,
  linkcolor=black,
  urlcolor=black
}

\titleformat{\section}
  {\large\bfseries}
  {}
  {0em}
  {}
  [\titlerule]

% ================== DOCUMENT ==================
\begin{document}

% ================== HEADER ==================
\begin{center}
  {\LARGE \textbf{FARIC FATHIAN HIDAYAH}}\\
  \vspace{4pt}
  \textbf{Fullstack Developer (Backend-Oriented)} \\
  \vspace{6pt}
  Bandung, West Java \,|\, 
  \href{mailto:faricfathianhidayah@gmail.com}{faricfathianhidayah@gmail.com} \,|\, 
  +62 881-7749-791 \\
  \href{https://github.com/faricfh}{github.com/faricfh} \,|\, 
  \href{https://portofolio-faricfh.vercel.app}{portofolio-faricfh.vercel.app}
\end{center}

% ================== PROFILE ==================
\section*{Professional Profile}
Fullstack Developer with more than 5 years of experience building and maintaining production-scale web applications for government institutions and state-owned enterprises. 
Specialized in backend architecture using Laravel and Yii2 as well as MySQL database optimization. Experienced in ensuring the stability and performance 
of more than 50 applications in production environments while handling the entire software development lifecycle \textit{end-to-end}.

% ================== TECHNICAL SKILLS ==================
\section*{Technical Skills}
\textbf{Backend:} PHP (Laravel, Yii2), REST API (20+ Endpoints), JWT Authentication, RBAC \\
\textbf{Frontend:} HTML, CSS, JavaScript (ES6+), React, Next.js, Tailwind CSS \\
\textbf{Database:} MySQL (Query Optimization, Indexing) \\
\textbf{Tools \& OS:} Git, GitHub, Postman, Linux (Ubuntu), Apache, VPS Deployment \\
\textbf{Familiar With:} Flutter (Dart), Kotlin

% ================== EXPERIENCE ==================
\section*{Work Experience}

\textbf{Fullstack Developer (Backend-Oriented)} \hfill \textit{Jun 2020 -- Present} \\
\textit{CV Putra Purnama Indonesia | Bandung | Full-time}
\begin{itemize}
    \item Responsible for technical maintenance and feature development across 50+ \textit{E-Government} application repositories used by various regional government institutions.
    \item Performed business logic customization and feature adaptations for each regional repository to meet local regulatory requirements without compromising core application integrity.
    \item Ensured code synchronization and stability across 50+ production environments through disciplined \textit{version control} practices and systematic debugging processes.
    \item Optimized MySQL query performance in high-volume data systems, resulting in an average application response speed improvement of 25\%.
    \item Designed and implemented 20+ REST API endpoints using Laravel/Yii2 for secure data integration between web application modules and mobile platforms.
\end{itemize}

\textbf{Freelance Fullstack Developer} \hfill \textit{Jul 2024 -- Jun 2025} \\
\textit{Client Projects via Fiverr | Remote | Freelance}
\begin{itemize}
    \item Developed custom Laravel-based web applications independently, from database schema design to \textit{deployment}, tailored to the specific needs of international clients.
    \item Managed ongoing maintenance cycles, optimized features, and developed additional functionalities that resulted in client repeat orders reaching 80\%+.
    \item Implemented an admin management system using AdminLTE and Role-Based Access Control (RBAC) to ensure data security within client applications.
\end{itemize}

\textbf{Programmer Intern (PKL)} \hfill \textit{Oct 2019 -- Nov 2019} \\
\textit{Solusi Teknis Bandung | Bandung | Internship}
\begin{itemize}
    \item Built a functional Laravel-based web application using the company’s real production database schema as part of an intensive system development training program.
    \item Successfully passed the \textit{functional testing} phase with senior developers according to the company’s defined quality standards.
\end{itemize}

% ================== PROJECTS ==================
\section*{Selected Projects}

\textbf{Fazdecore - Decoration Catalog Platform} \hfill \textit{Fullstack Developer}
\begin{itemize}
    \item Designed and developed a decoration service catalog platform independently using a \textit{decoupled architecture} with Laravel (REST API) and Next.js (\textit{Frontend} \& \textit{Admin Panel}).
    \item Developed a Next.js-based admin dashboard for centralized decoration data management, enabling real-time catalog content updates.
    \item Optimized application performance to achieve a page load time (\textit{Largest Contentful Paint}) of under 2 seconds.
    \item \href{https://fazdecore.com/}{fazdecore.com}
\end{itemize}

\textbf{Sali Insurance Management System} \hfill \textit{Fullstack Developer}
\begin{itemize}
    \item Designed and developed a custom insurance policy management system using Laravel to support the operational requirements of international clients.
    \item Built backend architecture and optimized MySQL database structures capable of handling thousands of policy data relationships with high data integrity.
    \item Implemented advanced security features and \textit{Role-Based Access Control} (RBAC) to protect sensitive customer information.
    \item \href{https://imas.sali.co.ke/}{imas.sali.co.ke}
\end{itemize}

\textbf{SIKAP - Employee Attendance System} \hfill \textit{Backend Developer}
\begin{itemize}
    \item Developed REST APIs to integrate attendance data between the Yii2 backend and Flutter mobile application in real-time.
    \item Adjusted employee allowance calculation logic based on updated regulations while maintaining historical data accuracy.
    \item Optimized large-scale data recap algorithms to ensure responsive report generation with low latency.
\end{itemize}

% ================== EDUCATION ==================
\section*{Education}
\textbf{SMK Assalaam Bandung} \hfill \textit{2017 -- 2020} \\
Software Engineering (RPL)

\end{document}